A Sample Document

### 2017-04-05 Writing/rsptime.tex
Update

%Experiment Result

>>>>

\subsubsection{PING Response Time Distribution}
%Experiment Result
PING is one of the most known ideal protocol for this attack. We measured its response time on CC2538 running Contiki OS. Since Contiki MAC\cite{ContikiMAC} sends duplicated PING requests, we define the PING Response Interval, PRI, to be the time between a PING response and its last paired request.

\Cref{ExamplePri} shows an example where Packet 205 and Packet 203 constitute a pair of PING packets, and their PRI is computed as their difference in time.

\begin{figure}[!h]
	\centering
	\includegraphics[width=\textwidth]{fig/PRI_hl.png}
	\caption{Example PRI\label{ExamplePri}}
\end{figure}

%Since the attack extracts the information contained in the extended response time of a specific request, the first problem is to see whether such extended response time can be filtered from normal ones.

\Cref{HelloworldPri} shows the histogram of PRIs collected for ``helloworld'' example from Contiki OS. Values $\geq$12ms are collected at 12ms. The result shows that the majority of PRIs are clustered around 9.5ms, whilst a clear gap exists between the majority and the outliers. The majority, which roughly ranged [9.0, 10.3]ms, corresponds to the case of Sensor Node 1 in \Cref{FingerprintTheory}.

\begin{figure}[!h]
	\centering
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width=\textwidth]{fig/helloworld_cc2538.png}
		\caption{PRIs of helloworld\label{HelloworldPri}}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width=\textwidth]{fig/helloworld_cc2538_outlier.png}
		\caption{PRIs outliers of helloworld\label{HelloworldPriOutliers}}
	\end{subfigure}
	\caption{PRIs for helloworld}
\end{figure}

We further plotted the upper outliers, which mostly ranged from [12, 2000]ms, in \Cref{HelloworldPriOutliers}. We suppose these outliers corresponds to the case of Sensor Node 2 in \Cref{FingerprintTheory} which PING request arrived when the processor was performing another task. We suppose the distribution of PRI shown in \Cref{HelloworldPriOutliers} is due to different tasks delays the PING request differently.

PRIs we collected on other applications showed the same characteristic. The majorities are clustered near a medium value. A clear proportion of outliers exists, leaving a clear gap between the majority. This implies that an adversary can easily draw a threshold by observing the distribution of PRIs to filter the ones corresponds to the extended response time. In our experiments the threshold is set to 12ms but any other values within the gap would also work.

\subsubsection{Matching Fingerprint}

%Comparing the distribution.
As of the hypothesis, we expect an distinctive outlier distribution to be used as a fingerprint of each different application.
